\documentclass{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{authblk} %package for blocking authors, followed by blocking affiliation
\usepackage{url}
\usepackage{ulem} % when using ulem package, must change \emph to \it for italics.
\usepackage{hyperref}
\usepackage{array}
\usepackage{amssymb,amsmath,tabu}
\usepackage{hyperref}
\usepackage[super]{nth}
\setlength\parindent{0pt}
\usepackage[english]{babel}


\begin{document}
\title{Homework 7\\ SOCI 502B: Graduate Statistics (Fall 2017) \\ {\large{10 points}} \\ {\large{Due: December 13, 2017}}}
\author[*]{}
\date{}
\maketitle



\section*{Overview:}
In this assignment, you'll be completing 1 question.

\subsection*{Problem 1 (\textit{Variables for Final Paper})}
For your final paper, you'll be selecting a minimum of three (3) variables from the GSS data set (or a data set you've already been using): two (2) independent variables (predictors) and one (1) dependent variable. Based on the coding/recoding of your dependent variable, you will select to employ either OLS/Multiple/Multivariate/Linear Regression or Binary Logistic/Logit Regression. 
\begin{itemize}
\item Dependent Variable:
\begin{itemize}
\item What is your dependent variable?
\item How is it coded?
\item Will you recode the variable? If so, how?
\end{itemize}
\item Independent Variables:
\begin{itemize}
\item What are two of your independent variables?
\item How are they coded?
\item Will you recode the variables? If so, how?
\end{itemize}
\item Analysis:
\begin{itemize}
\item What type of regression analysis will you conduct, and why?
\end{itemize}
\end{itemize}

\end{document}











