\documentclass{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{authblk} %package for blocking authors, followed by blocking affiliation
\usepackage{url}
\usepackage{ulem} % when using ulem package, must change \emph to \it for italics.
\usepackage{hyperref}
\usepackage{array}
\usepackage{amssymb,amsmath,tabu}
\usepackage[usenames, dvipsnames]{color}
\usepackage{hyperref}
\usepackage[super]{nth}
\setlength\parindent{0pt}
\usepackage[english]{babel}


\begin{document}
\title{Final Presentation and Paper\\ SOCI 502B: Graduate Statistics (Fall 2017)}
\author[*]{}
\date{}
\maketitle

The goal of this project is to demonstrate your knowledge of statistical methods, using GSS or some other data set\footnote{If not using GSS, make sure you've cleared the data set with me.} to answer a research question related to your interests. Students will select one of two multivariate techniques (OLS regression or logistic regression) to explain variation in some outcome variable of their choice. These multivariate models must include at least three (3) predictor (independent) variables. The selection of the \newline 

\begin{centering}
\section*{Data \& Methods, and Results Presentation (15 points)\\Due: 12/6}
\end{centering}

Students will be given the opportunity to present the Data \& Methods section and Results section of their final research papers. Students should treat the presentation like a brief, 5-10 minute conference talk. The presentation should: \\

\begin{itemize}
\item Present the research question being answered
\item Provide 1-2 theoretically-driven reasons why this is an important question and why certain variables (those which happen to be in the data set used) help you answer that question
\item Discuss the data source, the variables used, any manipulations to variables you conducted
\item Discuss the multivariate method applied to the data
\item Present and interpret the results along with an explanation for how you answered your research question
\end{itemize}

\begin{centering}
\section*{Final Data \& Methods, and Results Paper (15 points)\\Due: 12/13 @ 9:20pm}
\end{centering}

In a final paper, due the date and time of our final exam, students will complete a 3-5 page paper (double- or single-spaced, 8$\frac{1}{2}$ inch x 11 inch, 1 inch margins) that is only the Data \& Methods section and Results section of an empirical paper - a paper based on the multivariate statistical analysis of a data set they presented in class. In the final paper, students are required to: \\
\begin{itemize}
\item ``Restate'' their research question
\item Describe the data set (it's source, number of observations, the variables used for the analysis, any manipulation to variables or missingness in the data)
\item Describe the dependent variable, the key independent variables, and control variables
\item Discuss the multivariate method used to answer the research question
\item Explain and interpret of the results of the analysis
\item Conclude with a brief discussion/conclusion of the implications of the findings
\end{itemize}

This final paper is due (electronically) by 9:20pm on Wednesday, 12/13. No late papers will be accepted. \newline

\end{document}











