\documentclass{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{authblk} %package for blocking authors, followed by blocking affiliation
\usepackage{url}
\usepackage{ulem} % when using ulem package, must change \emph to \it for italics.
\usepackage{hyperref}
\usepackage{array}
\usepackage{amssymb,amsmath,tabu}
\usepackage{hyperref}
\usepackage[super]{nth}
\setlength\parindent{0pt}
\usepackage[english]{babel}


\begin{document}
\title{Homework 5\\ SOCI 502B: Graduate Statistics (Fall 2017) \\ {\large{10 points}} \\ {\large{Due: December 13, 2017}}}
\author[*]{}
\date{}
\maketitle



\section*{Overview:}
In this assignment, you'll be completing 1 problem using SPSS (or R). This problem covers topics from Chapter 8 in your textbook.

\subsection*{Problem 1 (\textit{Regression})}
\begin{itemize}
\item Using the GSS 2014 data set (\texttt{GSS2014\_final})\footnote{For SPSS, use \texttt{GSS2014\_final.sav}. For R, use the R script and \texttt{GSS2014\_final.csv}}, conduct a simple linear OLS regression analysis of how ``political (conservative) views'' (\texttt{polviews}) influence people's belief that the it is an important right for citizens to engage in civil disobedience when they oppose government actions (\texttt{oppsegov}\footnote{Higher scores indicate that people believe civil disobedience against the government is a very important right (e.g. must be protected)}). Hint: think about what is the independent variable and what is the dependent variable.
\begin{itemize}
\item \texttt{polviews} and \texttt{oppsegov} should be changed to scale measures
\end{itemize}
\item Next, conduct a multiple OLS regression by including the (\texttt{race}) variable as another predictor of people's belief that the it is an important right for citizens to engage in civil disobedience when they oppose government actions (\texttt{oppsegov}).
\item In this full (multiple regression) model, what is the value of the $R^{2}$ coefficient? How does it change from the initial (simple) model?
\item In this full (multiple regression) model, what is the value of the $F$ coefficient? How does it change from the initial (simple) model?
\item Correctly and fully report and interpret the full model statistics. Include variance explained ($R^{2}$, with interpretation), model fit ($F$, with interpretation), and the values/significance of each independent variable.
\end{itemize}

\end{document}











